Learning Network Size While Training with ShrinkNets

### 2018-02-08 paper/SysML/paper.tex

\author{Guillaume Leclerc, Raul Castro Fernandez, Samuel Madden}
\affiliation{%
  \institution{Massachussets Institute of Technology}
}
\email{[leclerc, raulcf, madden]@mit.edu}

@@

\section{Introduction}

When designing neural networks, one of the key parameters is the network size, i.e., 
%, number of layers
%and number of neuros per layer, 
%(width and depth)
the number of layers and neurons per layer.  Choosing these parameters appropriately
can dramatically affect performance, yet
%In particular, these hyper parameters have a strong correlation with
%over/underfitting \srm{give reference} \gl{I did some litterature review and
%actually this statement is quite controversial, should we rephrase ?}. 
there is no reliable way to efficiently set them. Although many search
 strategies and heuristics~\cite{Bengio2012a} have been proposed, including
%To select the best candidates, researchers have used strategies such
%as 
random search,
%\gl{Should we also move the references here if we remove the
%pargraph from the related work ?}, 
meta-gradient descent~\cite{Pedregosa2016},
Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}, 
%to find good parameters without exhaustively
%exploring the entire hyper-parameter space. 
 they generally require a compute-intensive
search of parameter space.

@@

We  implemented ShrinkNets, including the \emph{garbage collection}
mechanism on top of \textit{PyTorch}~\cite{paszke2017automatic}, and we have
made the software open source.\footnote{The code is available as Python/PyTorch
library on \url{http://github.com/mitdbg/fastdeepnets}
%\gl{Should we rename the repository ?}
}. We used used our implementation to evaluate two crucial aspects of
ShrinkNets, which we present next.

>>>>

\author{Guillaume Leclerc, Raul Castro Fernandez, Samuel Madden}
\affiliation{%
  \institution{Massachusetts Institute of Technology}
}
\email{[leclerc, raulcf, madden]@mit.edu}

@@

\section{Introduction}
Alternative intro sketch:
As neural networks become commodity in many applications from improving camera quality on mobile phones \cite{googleapple} over language translation \cite{languagetranslation} to text auto-complete \cite{autocomplete}, inference performance and model size become equally important to the quality of the prediction.  
Surprisingly, today those three concerns, quality, performance and model size, are largely handled separately with suboptimal results. 
That is, models are trained with a fixed architecture (e.g., considering a certain size and performance budget), but then during the training the network architecture is considered fixed and does not further improve.
In contrast, recently proposed techniques to make neural nets smaller after they have been trained, such as XX \cite{xx} and YY \cite{yy}, do not focus on the inference performance. 
In fact, besides universal applicable techniques such as quantitazation \cite{quant} and compiling neural networks to binary code to avoid unneccassary overhead, most existing techniques to make neural nets smaller actually harm performance as they often transform dense into sparse matrix multiplications, which is inherently slower to execute on modern hardware \cite{something}. 
%I am still not super happy with the flow. Will work on it more.

In this paper we present a new method to automatically tune the network size while training the model to drastically improve the inference performance with comparable quality to much larger networks  
The key idea is to
\emph{learn} the right network size at the same time that the network is
learning the main task. For example, for an image classification task, with our approach we can provide the training data to a network---without sizing it a priori---and expect to end up with a network that has learned to classify images with an accuracy similar to much larger network architectures.
Our approach has two main benefits. 
First, in contrast to existing neural network compression techniques, such as brain damage, it results in small dense models, which helps to improve inference performances
Second, and most surprisingly, the resulting models are often not only much smaller but also have better accuracy than much larger models.

Old intro:
When designing neural networks, one of the key parameters is the network size, i.e., 
%, number of layers
%and number of neuros per layer, 
%(width and depth)
the number of layers and neurons per layer.  Choosing these parameters appropriately
can dramatically affect performance, yet
%In particular, these hyper parameters have a strong correlation with
%over/underfitting \srm{give reference} \gl{I did some litterature review and
%actually this statement is quite controversial, should we rephrase ?}. 
there is no reliable way to efficiently set them. Although many search
 strategies and heuristics~\cite{Bengio2012a} have been proposed, including
%To select the best candidates, researchers have used strategies such
%as 
random search,
%\gl{Should we also move the references here if we remove the
%pargraph from the related work ?}, 
meta-gradient descent~\cite{Pedregosa2016},
Gaussian processes~\cite{Bergstra2011a}, and Parzen Estimators~\cite{Bergstra2011a}, 
%to find good parameters without exhaustively
%exploring the entire hyper-parameter space. 
 they generally require a compute-intensive
search of parameter space.

@@

We  implemented ShrinkNets, including the \emph{garbage collection}
mechanism on top of \textit{PyTorch}~\cite{paszke2017automatic}, and we have
made the software open source.\footnote{The code is available as Python/PyTorch
library on \url{http://github.com/mitdbg/fastdeepnets}
%\gl{Should we rename the repository ?}
}. We used our implementation to evaluate two crucial aspects of
ShrinkNets, which we present next.
